The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-15 src/ms.tex
rephrase to remove please request

The FITS standard was extended to rigorously describe time coordinates in the
WCS framework \citep{FITS-Time:2015}. Compared to
other types of coordinates in WCS, time requires more metadata: format, scale,
position, reference, etc. This metadata had to be manually specified and the
nuances understood by the user. \astropyfits could read this data as a standard
\astropyFitsColumn\, but would not interpret the time-related metadata and
attributes. Through the support of the
\href{https://summerofcode.withgoogle.com/archive/2017/projects/4778482366152704}{Google
Summer of Code} 2017 program,\footnote{To learn more about this project, please
see the final report
\href{https://aaryapatil.wordpress.com/2017/08/28/a-mixin-protocol-for-seamless-interoperability/}{A
mixin protocol for seamless interoperability}.} the \astropyfits package now
interprets time data correctly, using \astropyTime\ as a mixin column. For
backward compatibility, this feature may be turned off.

@@

We currently host 19 tutorials written as interactive Jupyter Notebooks and
rendered into static HTML pages with the infrastructure described above.
The tutorials span a range of astronomical topics, from general tasks like
reading or creating FITS files with different content or working with
astronomical coordinate systems, to more specific exercises like analyzing
spectroscopic data from the UVES instrument.
Now that the backend infrastructure is stable, we are interested in collecting
new content to serve and share: if you have ideas for contributions, or have
tutorials hosted on third-party sites that you would like to make searchable
through the Learn Astropy interface, please reach out by creating a \github
issue in the \href{https://github.com/astropy/astropy-tutorials}{Astropy
Tutorials repository}.
We currently host one Guide --- a longer-form walkthrough of a more complex
concept or topic --- that is focused on
\href{http://www.astropy.org/ccd-reduction-and-photometry-guide}{CCD image
reduction and photometry}, but are also actively seeking new material that would
be suitable for new guides.

>>>>

The FITS standard was extended to rigorously describe time coordinates in the
WCS framework \citep{FITS-Time:2015}. Compared to
other types of coordinates in WCS, time requires more metadata: format, scale,
position, reference, etc. This metadata had to be manually specified and the
nuances understood by the user. \astropyfits could read this data as a standard
\astropyFitsColumn\, but would not interpret the time-related metadata and
attributes. Through the support of the
\href{https://summerofcode.withgoogle.com/archive/2017/projects/4778482366152704}{Google
Summer of Code} 2017 program,\footnote{To learn more about this project,
see the final report
\href{https://aaryapatil.wordpress.com/2017/08/28/a-mixin-protocol-for-seamless-interoperability/}{A
mixin protocol for seamless interoperability}.} the \astropyfits package now
interprets time data correctly, using \astropyTime\ as a mixin column. For
backward compatibility, this feature may be turned off.

@@

We currently host 19 tutorials written as interactive Jupyter Notebooks and
rendered into static HTML pages with the infrastructure described above.
The tutorials span a range of astronomical topics, from general tasks like
reading or creating FITS files with different content or working with
astronomical coordinate systems, to more specific exercises like analyzing
spectroscopic data from the UVES instrument.
Now that the backend infrastructure is stable, we are interested in collecting
new content to serve and share.
Ideas for contributions, new tutorials, or suggestions for new tutorial series
to be made searchable through the Learn Astropy interface can be raised by
creating a \github issue in the
\href{https://github.com/astropy/astropy-tutorials}{Astropy Tutorials GitHub
repository}.
We currently host one Guide --- a longer-form walkthrough of a more complex
concept or topic --- that is focused on
\href{http://www.astropy.org/ccd-reduction-and-photometry-guide}{CCD image
reduction and photometry}, but are also actively seeking new material that would
be suitable for new guides.
